### 2016-04-28 docs/projectplan/projectplan.tex
first draft for the project plan

\documentclass[12pt, a4paper]{article}

\usepackage{amssymb, amsmath}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{url}

\author{Manuel Haid (1131404) \\ Thomas Mauerhofer (1031957) \\ Matthias Wölbitsch (1130899) \\ \\ Group 001}
\title{Project Plan for a Time Series Visualization Framework}
\date{}

\begin{document}

\maketitle

\section{Motivation}

In today's society data plays a import role in many different ways.
For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand.
Often time plays a essential role in these data sets. 
For example, the consumption of electricity does not only depend on the time of the day but also on the day of the week and other seasonal effects.
Such data sets are usually referred to as time series (i.e. two- or higher-dimensional data with time as one dimension).

When dealing with time series usually one of the first steps in the analysis process is the visualization of the data.
The graphical representation can already give some great insights in properties of the data.
For example, a simple visual inspection can already show some patterns, trends or seasonal effects without the use of statistical methods. 
These properties are important since they have to be considered in the modeling of the time series.
The goal of our project is to create a web-based framework that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.

\section{Project Description}

The time series visualization framework mainly consists of of a front-end and a back-end part.
This architectural design choice implies a clear separation of concerns. 
The back-end will be implemented in Python and is used for the processing of the data while the HTML/JavaScript front-end is used to present different views to the user.

One of the main responsibilities of the back-end application is the process of importing the data.
Currently we plan to provide three different ways to load data from an external source:

\begin{enumerate}
 \item \textbf{File import}: The most common way is a simple import of the data from files on the local file system.
 All supported import file formats are not specified yet, however, the usual formats such as \texttt{.csv} or \texttt{.tsv} should work with the application.
 \item \textbf{External APIs}: This import method could be used to easily explore data sets which are available on data set hosting sites. 
 For example, the well-known Time Series Data Library (TSDL) is hosted on \url{www.DataMarket.com} and could be accessed via an API. 
 \item \textbf{Sockets}: This import method could be used to explore data which is collected in real-time (e.g. sensor data). 
 However, further research is required to investigate the design of such interface for socket connections that provide data over time.
\end{enumerate}

After the time series data was imported it should be stored in a appropriate model. 
For this task we'll use the data analysis library pandas since it provides convenient high-performance data structures to store, access, and manipulate the data.
Other advantages of pandas are the support of operations on temporal data (e.g. slicing or filtering) and the support of other libraries (e.g. NumPy) for pandas data structures.

Another important part of the back-end is the visualization engine. 
Its main responsibility is the processing of the time series to create visualization primitives (i.e. it transforms the data into a representation that can later be rendered by the front-end).
The visualization engine provides a RESTful API for its functionality, which is another part of the back-end.
This allows the front-end to send simple HTTP requests to get visualizations of the time series.

\section{Timetable}

Table \ref{tab:timetable} shows some time estimates for the duration of different tasks from various areas of the project.

\begin{table}[h!]
\centering
\begin{tabular}{|l|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Task}} & \textbf{Duration [h]} \\ \hline
\textbf{Research} &  \\ \hline
  - foo sub tasks & 42 \\ \hline
  - bar sub tasks & 42 \\ \hline
\textbf{Other Task} &  \\ \hline
  - foo sub tasks & 42 \\ \hline
  - bar sub tasks & 42 \\ \hline
\end{tabular}
\caption{Estimation for various sub tasks of the project.}
\label{tab:timetable}
\end{table}

\section{Responsibilities}

\begin{description}
 \item[Manuel Haid] foo
 \item[Thomas Mauerhofer] bar
 \item[Matthias Wölbitsch] baz
\end{description}

\end{document}

### 2016-04-28 docs/projectplan/projectplan.tex
Added timetable

@@
 \textbf{Research} &  \\ \hline
-  - foo sub tasks & 42 \\ \hline
-  - bar sub tasks & 42 \\ \hline
-\textbf{Other Task} &  \\ \hline
-  - foo sub tasks & 42 \\ \hline
-  - bar sub tasks & 42 \\ \hline
+  - File import & 3 \\ \hline
+  - APIs & 5 \\ \hline
+  - Sockets & 10 \\ \hline
+  - Python libraries & 5 \\ \hline
+  - JavaScript visualization libraries & 5 \\ \hline
+\textbf{Implementation} &  \\ \hline
+  - User interface & 10 \\ \hline
+  - Import model & 5 \\ \hline
+  - Communication with APIs & 10 \\ \hline
+  - Sockets & 15 \\ \hline
+  - Generation of visualization primitives & 10 \\ \hline
+  - Visualization & 15 \\ \hline
+\textbf{Documentation} &  \\ \hline
+  - Code & 2 \\ \hline
+  - Projectplan & 10 \\ \hline
+  - Report & 10 \\ \hline
 \end{tabular}
@@
 \begin{description}
- \item[Manuel Haid] foo
- \item[Thomas Mauerhofer] bar
- \item[Matthias Wölbitsch] baz
+ \item[Manuel Haid]: user interface, import model
+ \item[Thomas Mauerhofer]: communication with APIs, visualization 
+ \item[Matthias Wölbitsch]: generation of visualization primitives, sockets
 \end{description}

### 2016-04-28 docs/projectplan/projectplan.tex
added description for some visualization primitives for the projectplan

--- 2016-04-28 docs/projectplan/projectplan.tex
@@
 Often time plays a essential role in these data sets. 
-For example, the consumption of electricity does not only depend on the time of the day but also on the day of the week and other seasonal effects.
+For example, the consumption of electricity does not only depend on the time of the day, but also on the day of the week and other seasonal effects.
 Such data sets are usually referred to as time series (i.e. two- or higher-dimensional data with time as one dimension).
@@
 The visualization engine provides a RESTful API for its functionality, which is another part of the back-end.
-This allows the front-end to send simple HTTP requests to get visualizations of the time series.
+This allows the front-end to send simple HTTP requests to get visualization primitives of the time series.
+To implement the API we'll use the Flask microframework which makes things like RESTful request dispatching quite easy.
+
+The front-end of the application is a simple HTML5 website that uses a JavaScript visualization library to display the visualization primitives.
+Which JavaScript visualization library will be used was not decided yet.
+However, a little bit of research showed that there plenty of different libraries available which support the plotting of temporal data.
+For example, two time series visualization libraries that are based on the well-known D3.js libary are Cubism.js and MetricsGraphics.js could be used for this project.
+Currently we plan to support the following visualization primitives which can be generated by the visualization engine and can be requested by the front-end:
+
+\begin{enumerate}
+ \item Simple time series graphs, which plot the observations (i.e. the data points) against the time of the observations.
+ \item Filters for the time series graphs, which allow the user to select only data in a certain time span.
+ \item Possibility to show multiple time series in the same figure or in linked figures.
+ \item Possibility to show the running average and running standard deviation of a time series (used to determine stationarity of a time series).
+ \item Time series graphs which are live updated whenever new data is available on a socket (i.e. live visualization of a time series).
+ \item Seasonal plots (i.e. plots where the data is plotted against the individual season in which it was observed).
+ \item Autocorrelation function (ACF) plots, which are a statistical tool to proof seasonal effects in the data.
+\end{enumerate}
+
+% TODO: visual evaluation of a model
 

### 2016-04-29 docs/projectplan/projectplan.tex
finished project plan

@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{hyperref}
@@
 \author{Manuel Haid (1131404) \\ Thomas Mauerhofer (1031957) \\ Matthias Wölbitsch (1130899) \\ \\ Group 001}
-\title{Project Plan for a Time Series Visualization Framework}
+\title{Project Plan for \texttt{timeline}: a Time Series Visualization Framework}
 \date{}
@@
 The graphical representation can already give some great insights in properties of the data.
-For example, a simple visual inspection can already show some patterns, trends or seasonal effects without the use of statistical methods. 
-These properties are important since they have to be considered in the modeling of the time series.
+For example, a simple visual inspection can show patterns, trends or seasonal effects without the use of advanced statistical methods. 
+These properties are important since they have to be considered in the modeling of the time series (e.g. in forecasting models).
 The goal of our project is to create a web-based framework that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.
@@
  \item \textbf{Sockets}: This import method could be used to explore data which is collected in real-time (e.g. sensor data). 
- However, further research is required to investigate the design of such interface for socket connections that provide data over time.
+ However, further research is required to investigate the design of such interface for socket connections that provide data over time (e.g. sampling, \ldots).
 \end{enumerate}
 
-After the time series data was imported it should be stored in a appropriate model. 
+After the time series data was imported it should be stored in a appropriate data model. 
 For this task we'll use the data analysis library pandas since it provides convenient high-performance data structures to store, access, and manipulate the data.
-Other advantages of pandas are the support of operations on temporal data (e.g. slicing or filtering) and the support of other libraries (e.g. NumPy) for pandas data structures.
+Other advantages of pandas are the support of operations on temporal data (e.g. slicing, filtering, \ldots) and the support of other libraries (e.g. NumPy) for pandas data structures.
 
 Another important part of the back-end is the visualization engine. 
-Its main responsibility is the processing of the time series to create visualization primitives (i.e. it transforms the data into a representation that can later be rendered by the front-end).
+Its main responsibility is the processing of the time series to create visualization primitives (i.e.
+it transforms the data stored in the model into representations that can later be rendered by the front-end).
 The visualization engine provides a RESTful API for its functionality, which is another part of the back-end.
@@
 Which JavaScript visualization library will be used was not decided yet.
-However, a little bit of research showed that there plenty of different libraries available which support the plotting of temporal data.
+However, a little bit of research showed that there plenty of different libraries available that support the plotting of temporal data.
 For example, two time series visualization libraries that are based on the well-known D3.js libary are Cubism.js and MetricsGraphics.js could be used for this project.
-Currently we plan to support the following visualization primitives which can be generated by the visualization engine and can be requested by the front-end:
+Currently we plan to support the following visualization primitives which can be generated by the visualization engine and rendered by the front-end:
 
@@
  \item Simple time series graphs, which plot the observations (i.e. the data points) against the time of the observations.
- \item Filters for the time series graphs, which allow the user to select only data in a certain time span.
- \item Possibility to show multiple time series in the same figure or in linked figures.
- \item Possibility to show the running average and running standard deviation of a time series (used to determine stationarity of a time series).
+ \item Filtered time series graphs, which allow the user to select data in a certain time span or with other distinct attributes.
+ \item Possibility to show multiple different time series in the same figure or in linked figures (see \autoref{fig:time_series_plots}).
+ \item Possibility to show the running average and running standard deviation of a time series in a time graph (used to determine stationarity of a time series).
  \item Time series graphs which are live updated whenever new data is available on a socket (i.e. live visualization of a time series).
- \item Seasonal plots (i.e. plots where the data is plotted against the individual season in which it was observed).
- \item Autocorrelation function (ACF) plots, which are a statistical tool to proof seasonal effects in the data.
+ \item Seasonal plots (i.e. plots in which the data is plotted against the individual season in which it was observed).
+ \item Autocorrelation function (ACF) plots, which are a statistical tool to proof seasonal effects in the data (see \autoref{fig:acf}).
+ \item Forecasting model evaluation plots that highlight three different parts of model in a time series graph:
+ \begin{enumerate}
+  \item The section of the time series that was used as training data for the model.
+  \item The forecasted time series including a confidence interval up to the horizon of the prediction.
+  \item The real values of the time series for the forecasted interval if available.
+ \end{enumerate}
 \end{enumerate}
 
-% TODO: visual evaluation of a model
+\begin{figure}[ht!]
+  \centering
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{images/timeplot.png}
+    \caption{Exemplary time series plot that shows three different data sets.}
+    \label{fig:time_series_plots}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{images/acf.png}
+    \caption{An exemplary autocorrelation function plot that shows seasonal patterns.}
+    \label{fig:acf}
+  \end{subfigure}
+  \caption{Examples for different visualizations of time series.}
+\end{figure}
 
@@
 
-Table \ref{tab:timetable} shows some time estimates for the duration of different tasks from various areas of the project.
+\autoref{tab:timetable} shows some time estimates for the duration of different tasks from various areas of the project.
 
-\begin{table}[h!]
+\begin{table}[ht!]
 \centering

### 2016-04-29 docs/projectplan/projectplan.tex
some minor changes in the project plan

@@
 \author{Manuel Haid (1131404) \\ Thomas Mauerhofer (1031957) \\ Matthias Wölbitsch (1130899) \\ \\ Group 001}
-\title{Project Plan for \texttt{timeline}: a Time Series Visualization Framework}
+\title{Project Plan for \texttt{timeline}: a Time Series Visualization Platform}
 \date{}
@@
 These properties are important since they have to be considered in the modeling of the time series (e.g. in forecasting models).
-The goal of our project is to create a web-based framework that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.
+The goal of our project is to create a web-based platform that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.
 
@@
 
-The time series visualization framework mainly consists of of a front-end and a back-end part.
+The time series visualization platform mainly consists of of a front-end and a back-end part.
 This architectural design choice implies a clear separation of concerns. 
@@
 The front-end of the application is a simple HTML5 website that uses a JavaScript visualization library to display the visualization primitives.
-Which JavaScript visualization library will be used was not decided yet.
+Which library will be used was not decided yet.
 However, a little bit of research showed that there plenty of different libraries available that support the plotting of temporal data.
-For example, two time series visualization libraries that are based on the well-known D3.js libary are Cubism.js and MetricsGraphics.js could be used for this project.
+For example, two time series visualization libraries, that are based on the well-known D3.js libary, are Cubism.js and MetricsGraphics.js could be used for this project.
 Currently we plan to support the following visualization primitives which can be generated by the visualization engine and rendered by the front-end:

### 2016-05-03 bin/copy_files_to_server.sh
Added Vagrantfiles

@@ -1,0 +1,26 @@
+#!/bin/sh
+if cd "`dirname \"$0\"`"; then
+    absdirpath=`pwd`
+    cd "$OLDPWD" || exit 1
+else
+    exit 1
+fi
+SCRIPTDIR=$absdirpath
+BASEDIR=$(dirname $SCRIPTDIR)
+SCRIPTNAME=$(basename $0 .sh)
+
+echo ""
+echo "===== $SCRIPTNAME ====="
+echo ""
+
+echo "remove old files..."
+rm -rf ../vagrant/src/*
+
+echo "copy files"
+cp -R ../src/. ../vagrant/src/
+
+cd ../vagrant
+vagrant ssh -c "/vagrant/config/service/start_backend.sh"
+
+
+

### 2016-05-03 bin/start_ipython.sh

@@ -1,0 +1,22 @@
+#!/bin/sh
+if cd "`dirname \"$0\"`"; then
+    absdirpath=`pwd`
+    cd "$OLDPWD" || exit 1
+else
+    exit 1
+fi
+SCRIPTDIR=$absdirpath
+BASEDIR=$(dirname $SCRIPTDIR)
+SCRIPTNAME=$(basename $0 .sh)
+
+echo ""
+echo "===== $SCRIPTNAME ====="
+echo ""
+
+cd ../vagrant/
+
+vagrant ssh -c "/vagrant/config/service/start_ipython.sh"
+
+
+
+

### 2016-05-03 src/hello.py

@@ -1,0 +1,29 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+# <codecell>
+
+from pandas import *
+import numpy as np
+from flask import Flask
+app = Flask(__name__)
+
+@app.route('/')
+def hello_world():
+    return 'Hello World!'
+
+if __name__ == '__main__':
+    app.run(host='0.0.0.0', debug=True, port=4242, use_reloader=True)
+
+def shutdown_server():
+    func = request.environ.get('werkzeug.server.shutdown')
+    if func is None:
+        raise RuntimeError('Not running with the Werkzeug Server')
+    func()
+
+@app.route('/shutdown')
+def shutdown():
+    shutdown_server()
+    return 'Server shutting down...'
+
+

### 2016-05-03 vagrant/config/service/start_backend.sh

@@ -1,0 +1,18 @@
+#!/bin/sh
+
+if cd "`dirname \"$0\"`"; then
+    absdirpath=`pwd`
+    cd "$OLDPWD" || exit 1
+else
+    exit 1
+fi
+SCRIPTDIR=$absdirpath
+BASEDIR=$(dirname $SCRIPTDIR)
+SCRIPTNAME=$(basename $0 .sh)
+
+echo ""
+echo "===== $SCRIPTNAME ====="
+echo ""
+
+python3 hello.py
+

### 2016-05-03 vagrant/config/service/start_ipython.sh

@@ -1,0 +1,18 @@
+#!/bin/sh
+
+if cd "`dirname \"$0\"`"; then
+    absdirpath=`pwd`
+    cd "$OLDPWD" || exit 1
+else
+    exit 1
+fi
+SCRIPTDIR=$absdirpath
+BASEDIR=$(dirname $SCRIPTDIR)
+SCRIPTNAME=$(basename $0 .sh)
+
+echo ""
+echo "===== $SCRIPTNAME ====="
+echo ""
+
+ipython3 notebook --ip=0.0.0.0
+

### 2016-05-03 vagrant/config/shell/custom.sh

@@ -1,0 +1,96 @@
+#!/bin/sh
+if cd "`dirname \"$0\"`"; then
+    absdirpath=`pwd`
+    cd "$OLDPWD" || exit 1
+else
+    exit 1
+fi
+SCRIPTDIR=$absdirpath
+BASEDIR=$(dirname $SCRIPTDIR)
+SCRIPTNAME=$(basename $0 .sh)
+
+echo ""
+echo "===== $SCRIPTNAME ====="
+echo ""
+
+# NOTE: this script will run as root !
+
+echo "add here your install commands.."
+
+##e.g. add database
+#mysql -u root -p"vagrant" -e ";CREATE DATABASE myapp; GRANT ALL ON myapp.* TO myapp@localhost IDENTIFIED BY 'mypass';FLUSH PRIVILEGES;"
+
+
+## use this for php applications
+### add apache config
+#cp /vagrant/config/files/apache/myphpapp.conf /etc/apache2/sites-available/myapp.conf
+### activate apache conf
+#a2ensite myapp.conf
+
+
+
+### copy application files 
+#cp -R /git_home/src/. /home/vagrant/
+### set rights
+chown -R vagrant:vagrant /home/vagrant/
+
+
+
+## use this for tomcat applications
+### add apache config
+#cp /vagrant/config/files/apache/mytomcatapp.conf /etc/apache2/sites-available/myapp.conf
+### activate apache conf
+#a2ensite myapp.conf
+### add tomcat instance under /home/vagrant/tomcat
+#su vagrant -c "cd ~/ && tomcat7-instance-create tomcat"
+### change tomcatconfig
+#cp /vagrant/config/files/tomcat/server.xml tomcat/conf/server.xml
+#sed -i -e 's/JAVA_OPTS="-Djava.awt.headless=true -Xmx128M"/JAVA_OPTS="-Djava.awt.headless=true -Xmx512M"/' /home/vagrant/tomcat/bin/setenv.sh
+### copy application files 
+#cp -R /vagrant_data/example/java /home/vagrant/tomcat/webapps/ROOT
+### set rights
+#chown -R vagrant:vagrant /home/vagrant/tomcat/webapps
+#chown vagrant:vagrant /home/vagrant/tomcat/conf/server.xml
+#chown vagrant:vagrant /home/vagrant/tomcat/bin/setenv.sh
+### start tomcat
+#su vagrant -c "cd ~/tomcat && ./bin/startup.sh"
[…]

### 2016-05-03 vagrant/config/shell/lamp_base.sh

@@ -1,0 +1,72 @@
+#!/bin/sh
+if cd "`dirname \"$0\"`"; then
+    absdirpath=`pwd`
+    cd "$OLDPWD" || exit 1
+else
+    exit 1
+fi
+SCRIPTDIR=$absdirpath
+BASEDIR=$(dirname $SCRIPTDIR)
+SCRIPTNAME=$(basename $0 .sh)
+
+echo ""
+echo "===== $SCRIPTNAME ====="
+echo ""
+
+## PACKAGES
+
+DEPENDENCIES_BASE="curl zip bzip2 vim lynx ntp git subversion git-svn"
+DEPENDENCIES_APACHE="apache2"
+DEPENDENCIES_PHP="php5 php5-mysql php5-curl php5-gd php5-mcrypt"
+DEPENDENCIES_PYTHON="python python3-pip python3-matplotlib python3-pandas ipython3-browser python-pygraphviz python-virtualenv libapache2-mod-wsgi"
+DEPENDENCIES_JAVA="openjdk-6-jdk"
+DEPENDENCIES_TOMCAT="tomcat7-user libapache2-mod-jk"
+DEPENDENCIES_MYSQL="mysql-server phpmyadmin"
+
+
+## configuration for mysql
+#echo mysql-server mysql-server/root_password select "vagrant" | debconf-set-selections
+#echo mysql-server mysql-server/root_password_again select "vagrant" | debconf-set-selections
+
+## configuration for phpmyadmin
+#echo 'phpmyadmin phpmyadmin/dbconfig-install boolean false' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/reconfigure-webserver multiselect apache2' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/app-password-confirm password vagrant' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/mysql/admin-pass password vagrant' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/password-confirm password vagrant' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/setup-password password vagrant' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/database-type select mysql' | debconf-set-selections
+#echo 'phpmyadmin phpmyadmin/mysql/app-pass password vagrant' | debconf-set-selections
+#echo 'dbconfig-common dbconfig-common/mysql/app-pass password vagrant' | debconf-set-selections
[…]

### 2016-06-09 timeline/api.py
major refactoring

@@ -3,7 +3,7 @@
 import json
 from datetime import datetime
 from flask import Blueprint, request, Response, abort
-from data_import import get_data_set, get_live_data_set, get_forecast_data_set
+from data_sets import get_data_set, get_live_data_set, get_forecast
 from visualizations import (
     time_series_plot, add_rolling_mean, add_rolling_std, auto_correlation_plot,
     forecasting_eval_plot, build_data_object
@@ -12,33 +12,31 @@ from visualizations import (
 
 api = Blueprint('api', __name__)
 
-@api.route('/time_plot', defaults={'data_set_id': 'random'})
 @api.route('/time_plot/<data_set_id>')
 def time_plot(data_set_id):
-    # TODO: error handling for invalid data set id
-    data_set = get_data_set(data_set_id)
+    try:
+        data_set = get_data_set(data_set_id)
+    except KeyError:
+        abort(404)
 
-    if request.args.get('start_date', None):
-        start = datetime.fromtimestamp(int(request.args.get('start_date')))
-        data_set['data'] = data_set['data'][start:]
+    start = datetime.fromtimestamp(int(request.args.get('start_date'))) \
+        if 'start_date' in request.args else None
+    end = datetime.fromtimestamp(int(request.args.get('end_date'))) \
+        if 'end_date' in request.args else None
 
-    if request.args.get('end_date', None):
-        end = datetime.fromtimestamp(int(request.args.get('end_date')))
-        data_set['data'] = data_set['data'][:end]
+    viz = time_series_plot(data_set, start, end, area=False)
 
-    viz = time_series_plot(data_set, area=False)
-
-    if request.args.get('rolling_mean_window', None):
+    if 'rolling_mean_window' in request.args:
         try:
             window = int(request.args.get('rolling_mean_window'))
-            add_rolling_mean(data_set, viz=viz, window=window)
+            add_rolling_mean(data_set, viz, window, start, end)
         except ValueError:
             abort(400)
 
-    if request.args.get('rolling_std_window', None):
+    if 'rolling_std_window' in request.args:
         try:
             window = int(request.args.get('rolling_std_window'))
-            add_rolling_std(data_set, viz=viz, window=window)
+            add_rolling_std(data_set, viz, window, start, end)
         except ValueError:
             abort(400)
 
@@ -46,21 +44,26 @@ def time_plot(data_set_id):
 
 @api.route('/time_plots')
[…]

### 2016-06-09 timeline/app.py

@@ -4,6 +4,8 @@
 from flask import Flask
 from frontend import frontend
 from api import api
+import example_data_sets as examples
+import data_sets
 
 
 app = Flask(__name__)
@@ -11,4 +13,10 @@ app.register_blueprint(frontend)
 app.register_blueprint(api, url_prefix='/api')
 
 if __name__ == '__main__':
+    data_sets.register_data_set(examples.generate_random_data_set())
+    data_sets.register_data_set(examples.generate_random_data_set())
+    data_sets.register_data_set(examples.load_internet_traffic_data_set())
+    data_sets.register_live_data_set(examples.generate_random_live_data_set())
+    data_sets.register_forecast(examples.generate_internet_traffic_forecast())
+
     app.run(host='0.0.0.0', debug=True)

### 2016-06-09 timeline/data_import.py

@@ -1,181 +1,0 @@
-#!/usr/bin/env python3
-# encoding: utf-8
-
-import threading
-import time
-import queue
-import datetime
-
-import pandas as pd
-import numpy as np
-import glob
-
-class LiveRandomData(object):
-    def __init__(self):
-        self.ts = pd.Series()
-        self.queue = queue.Queue()
-
-        generator = threading.Thread(target=self._data_generator)
-        generator.daemon=True
-        generator.start()
-
-    def get_data_set(self):
-        while True:
-            try:
-                time_stamp, data = self.queue.get(block=False)
-                self.ts[time_stamp] = data
-            except queue.Empty:
-                break
-
-        return {
-            'id': 0,
-            'name': 'Live Random Time Series',
-            'legend': 'live data',
-            'description': 'Random data which is generated on the fly.',
-            'data': self.ts
-        }
-
-    def _data_generator(self):
-        mu = np.random.randint(0, 11)
-        sigma = np.random.ranf() * 2
-        while True:
-            data_point = sigma * np.random.randn() + mu
-            self.queue.put((datetime.datetime.now(), data_point))
-            time.sleep(1)
-
-live_random_data = LiveRandomData()
-
-class csvData:
-
-    data = []
-
-    def __init__(self, name, description, isForecast):
-        self.name = name
-        self.description = description
-        self.isForecast = isForecast
-
-    def add_data(self, data):
-        self.data.append(data)
-
-def get_data_set_from_folder():
-    csvMap = {}
-    counter = 0
-
-    for fileName in glob.glob('../datasets/*.csv'):
-
-        print(fileName)
-
-        data = pd.read_csv(fileName, parse_dates='Time', index_col='Time', comment='#')
-        data = data / 8 / 2**30 # convert bits into GB
-        data.rename(columns={'Internet traffic data (in bits)':
-                             'Internet traffic data (in GB)'}, inplace=True)
-
-        i = 0
-        with open(fileName) as f:
-            for line in f:
-                if line.startswith('#'):
-                    comment = line.split(':')
-
-                    if comment[0] == "#name":
-                        name = comment[1]
-                    elif comment[0] == "#description":
-                        description = comment[1]
-                    elif comment[0] == "#isForecast":
-                        isForecast = comment[1]
[…]

### 2016-06-09 timeline/data_sets.py

@@ -1,0 +1,78 @@
+#!/usr/bin/env python3
+# encoding: utf-8
+
+import uuid
+from threading import Lock
+import pandas as pd
+
+
+forecasts = dict()
+time_series = dict()
+live_time_series = dict()
+
+def register_data_set(data_set):
+    time_series[data_set.id] = data_set
+
+def register_live_data_set(data_set):
+    live_time_series[data_set.id] = data_set
+
+def register_forecast(forecast):
+    forecasts[forecast.id] = forecast
+
+def get_data_set(data_set_id):
+    ts = time_series.get(data_set_id)
+    if not ts:
+        raise KeyError('No data set with such ID.')
+    return ts
+
+def get_live_data_set(data_set_id):
+    ts = live_time_series.get(data_set_id)
+    if not ts:
+        raise KeyError('No live data set with such ID.')
+    return ts
+
+def get_forecast(forecast_id):
+    forecast = forecasts.get(forecast_id)
+    if not forecast:
+        raise KeyError('No forecast with such ID.')
+    return forecast
+
+def get_all_data_sets():
+    return time_series.values()
+
+def get_all_live_data_sets():
+    return live_time_series.values()
+
+def get_all_forecasts():
+    return forecasts.values()
+
+class TimeSeries(object):
+    def __init__(self, name, description, ts, legend=None):
+        self.id = str(uuid.uuid4())
+        self.name = name
+        self.description = description
+        self.data = ts
+        self.legend = name if legend is None else legend
+
+class LiveTimeSeries(TimeSeries):
+    def __init__(self, name, description, legend=None):
+        TimeSeries.__init__(self, name, description, pd.Series(), legend=legend)
+        self.mutex = Lock()
+
+    def get_data(self, start=None, end=None):
+        with self.mutex:
+            ts = self.data if start is None else self.data[start:]
+            ts = ts if end is None else ts[:end]
+            return ts
+
+    def update_data(self, *args, **kwargs):
+        raise NotImplementedError
+
+class TimeSeriesForecast(TimeSeries):
+    def __init__(self, name, description, training_data, forcasted_data,
+                 test_data=None, validation_split=None):
+        TimeSeries.__init__(self, name, description, training_data, '.legend')
+        self.training_data = training_data
+        self.forcasted_data = forcasted_data
+        self.test_data = test_data
+        self.validation_split = validation_split

### 2016-06-09 timeline/example_data_sets.py

@@ -1,0 +1,83 @@
+#!/usr/bin/env python3
+# encoding: utf-8
+
+import threading
+import datetime
+import time
+import pandas as pd
+import numpy as np
+from data_sets import TimeSeries, LiveTimeSeries, TimeSeriesForecast
+
+
+class LiveRandomData(LiveTimeSeries):
+    def __init__(self):
+        LiveTimeSeries.__init__(self, 'Live Random Time Series',
+            'Random data which is generated on the fly.', 'live data')
+
+        generator = threading.Thread(target=self.update_data)
+        generator.daemon=True
+        generator.start()
+
+    def update_data(self, *args, **kwargs):
+        mu = np.random.randint(0, 11)
+        sigma = np.random.ranf() * 2
+        while True:
+            timestamp = datetime.datetime.now()
+            data_point = sigma * np.random.randn() + mu
+            with self.mutex:
+                self.data[timestamp] = data_point
+            time.sleep(1)
+
+def generate_random_live_data_set():
+    return LiveRandomData()
+
+def generate_internet_traffic_forecast():
+    data = pd.read_csv('../datasets/internet-traffic-data.csv',
+        parse_dates='Time', index_col='Time')
+    data = data / 8 / 2**30 # convert bits into GB
+    data.rename(columns={'Internet traffic data (in bits)': 'GB'},
+        inplace=True)
+
+    training_set = data['GB'][:'2005-07-13 23:59:59'].copy()
+    test_set = data['GB']['2005-07-14 00:00:00':].copy()
+    forecast_data = data['2005-07-14 00:00:00':].copy()
+    forecast_data.rename(columns={'GB': 'value'}, inplace=True)
+    forecast_data['value'] = 0.5
+    forecast_data['lower bound'] = forecast_data['value'] * 0.90
+    forecast_data['upper bound'] = forecast_data['value'] * 1.10
+
+    return TimeSeriesForecast('Internet Traffic Forecast', 'A exemplary \
+        forecast of the internet traffic of a private ISP.', training_set,
+        forecast_data, test_data=test_set, validation_split=1120780799)
+
+def load_internet_traffic_data_set():
+    data = pd.read_csv('../datasets/internet-traffic-data.csv',
+        parse_dates='Time', index_col='Time')
+    data = data / 8 / 2**30 # convert bits into GB
+    data.rename(columns={'Internet traffic data (in bits)':
+                         'Internet traffic data (in GB)'}, inplace=True)
+
[…]

### 2016-06-09 timeline/frontend.py

@@ -1,9 +1,9 @@
 # encoding: utf-8
 
 from flask import Blueprint, render_template
-from data_import import (
-    get_data_set, get_live_data_set, get_forecast_data_set, get_all_data_sets,
-    get_all_live_data_sets, get_all_eval_forecast_data_sets
+from data_sets import (
+    get_data_set, get_live_data_set, get_forecast, get_all_data_sets,
+    get_all_live_data_sets, get_all_forecasts
 )
 
 frontend = Blueprint('profile', __name__)
@@ -37,7 +37,7 @@ def live_info(data_set_id):
 def eval_info(data_set_id):
     return render_template(
         'eval_info.html',
-        data_set=get_forecast_data_set(data_set_id)
+        data_set=get_forecast(data_set_id)
     )
 
 @frontend.route('/')
@@ -46,5 +46,5 @@ def index():
         'index.html',
         data_sets=get_all_data_sets(),
         live_data_sets=get_all_live_data_sets(),
-        eval_data_sets=get_all_eval_forecast_data_sets()
+        eval_data_sets=get_all_forecasts()
     )

### 2016-06-09 timeline/visualizations.py

@@ -4,31 +4,38 @@
 import numpy as np
 
 
-def time_series_plot(data_sets, **kwargs):
+def time_series_plot(data_sets, start_date=None, end_date=None, **kwargs):
     data = []
     legend = []
 
-    if type(data_sets) == dict:
+    if type(data_sets) != list:
         data_sets = [data_sets]
 
     for data_set in data_sets:
-        data.append(build_data_object(data_set['data']))
-        legend.append(data_set['legend'])
+        ts = data_set.data if start_date is None else data_set.data[start_date:]
+        ts = ts if end_date is None else ts[:end_date]
+        data.append(build_data_object(ts))
+        legend.append(data_set.legend)
 
-    title = data_sets[0]['name'] if len(data_sets) == 1 else ''
+    title = data_sets[0].name if len(data_sets) == 1 else ''
 
-    return {'title': title, 'x_accessor': 'date',
-            'y_accessor': 'value', 'data': data, 'legend': legend,
-            **kwargs}
+    return {'title': title, 'x_accessor': 'date', 'y_accessor': 'value',
+            'data': data, 'legend': legend, **kwargs}
 
-def add_rolling_mean(data_set, viz, window):
-    rolling_mean_ts = data_set['data'].rolling(window=window).mean().dropna()
+def add_rolling_mean(data_set, viz, window, start_date=None, end_date=None):
+    ts = data_set.data if start_date is None else data_set.data[start_date:]
+    ts = ts if end_date is None else ts[:end_date]
+
+    rolling_mean_ts = ts.rolling(window=window).mean().dropna()
     data = build_data_object(rolling_mean_ts)
     viz['data'].append(data)
     viz['legend'].append('mean')
 
-def add_rolling_std(data_set, viz, window):
-    rolling_std_ts = data_set['data'].rolling(window=window).std().dropna()
+def add_rolling_std(data_set, viz, window, start_date=None, end_date=None):
+    ts = data_set.data if start_date is None else data_set.data[start_date:]
+    ts = ts if end_date is None else ts[:end_date]
+
+    rolling_std_ts = ts.rolling(window=window).std().dropna()
     data = build_data_object(rolling_std_ts)
     viz['data'].append(data)
     viz['legend'].append('std')
@@ -36,13 +43,13 @@ def add_rolling_std(data_set, viz, window):
 def auto_correlation_plot(data_set, max_lag, **kwargs):
     z95 = 1.9599639845400540 # z-score for 0.95 of N(0,1)
[…]

### 2016-06-09 docs/report/paper.tex
added stub for project report

%"runningheads" enables:
%  - page number on page 2 onwards
%  - title/authors on even/odd pages
%This is good for other readers to enable proper archiving among other papers and pointing to content.
%Even if the title page states the title, when printed and stored in a folder, when blindly opening the folder, one could hit not the title page, but an arbitrary page. Therefore, it is good to have title printed on the pages, too.
\documentclass[runningheads,a4paper]{llncs}

%Even though `american`, `english` and `USenglish` are synonyms for babel package (according to https://tex.stackexchange.com/questions/12775/babel-english-american-usenglish), the llncs document class is prepared to avoid the overriding of certain names (such as "Abstract." -> "Abstract" or "Fig." -> "Figure") when using `english`, but not when using the other 2.
\usepackage[english]{babel}

%better font, similar to the default springer font
%cfr-lm is preferred over lmodern. Reasoning at http://tex.stackexchange.com/a/247543/9075
\usepackage[%
rm={oldstyle=false,proportional=true},%
sf={oldstyle=false,proportional=true},%
tt={oldstyle=false,proportional=true,variable=true},%
qt=false%
]{cfr-lm}
%
%if more space is needed, exchange cfr-lm by mathptmx
%\usepackage{mathptmx}

\usepackage{graphicx}

%extended enumerate, such as \begin{compactenum}
\usepackage{paralist}

%put figures inside a text
%\usepackage{picins}
%use
%\piccaptioninside
%\piccaption{...}
%\parpic[r]{\includegraphics ...}
%Text...

%Sorts the citations in the brackets
%\usepackage{cite}

\usepackage[T1]{fontenc}

%for demonstration purposes only
\usepackage[math]{blindtext}

%for easy quotations: \enquote{text}
\usepackage{csquotes}

%enable margin kerning
\usepackage{microtype}

%tweak \url{...}
\usepackage{url}
%nicer // - solution by http://tex.stackexchange.com/a/98470/9075
\makeatletter
\def\Url@twoslashes{\mathchar`\/\@ifnextchar/{\kern-.2em}{}}
\g@addto@macro\UrlSpecials{\do\/{\Url@twoslashes}}
\makeatother
\urlstyle{same}
%improve wrapping of URLs - hint by http://tex.stackexchange.com/a/10419/9075
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

%diagonal lines in a table - http://tex.stackexchange.com/questions/17745/diagonal-lines-in-table-cell
%slashbox is not available in texlive (due to licensing) and also gives bad results. This, we use diagbox
%\usepackage{diagbox}

%required for pdfcomment later
\usepackage{xcolor}

% new packages BEFORE hyperref
% See also http://tex.stackexchange.com/questions/1863/which-packages-should-be-loaded-after-hyperref-instead-of-before

%enable hyperref without colors and without bookmarks
\usepackage[
%pdfauthor={},
%pdfsubject={},
%pdftitle={},
%pdfkeywords={},
bookmarks=false,
breaklinks=true,
colorlinks=true,
linkcolor=black,
citecolor=black,
urlcolor=black,
%pdfstartpage=19,
pdfpagelayout=SinglePage,
pdfstartview=Fit
]{hyperref}
%enables correct jumping to figures when referencing
\usepackage[all]{hypcap}

%enable nice comments
\usepackage{pdfcomment}
\newcommand{\commentontext}[2]{\colorbox{yellow!60}{#1}\pdfcomment[color={0.234 0.867 0.211},hoffset=-6pt,voffset=10pt,opacity=0.5]{#2}}
\newcommand{\commentatside}[1]{\pdfcomment[color={0.045 0.278 0.643},icon=Note]{#1}}

%compatibality with TODO package
\newcommand{\todo}[1]{\commentatside{#1}}

%enable \cref{...} and \Cref{...} instead of \ref: Type of reference included in the link
\usepackage[capitalise,nameinlink]{cleveref}
%Nice formats for \cref
\crefname{section}{Sect.}{Sect.}
\Crefname{section}{Section}{Sections}

\usepackage{xspace}
%\newcommand{\eg}{e.\,g.\xspace}
%\newcommand{\ie}{i.\,e.\xspace}
\newcommand{\eg}{e.\,g.,\ }
\newcommand{\ie}{i.\,e.,\ }

%introduce \powerset - hint by http://matheplanet.com/matheplanet/nuke/html/viewtopic.php?topic=136492&post_id=997377
\DeclareFontFamily{U}{MnSymbolC}{}
\DeclareSymbolFont{MnSyC}{U}{MnSymbolC}{m}{n}
\DeclareFontShape{U}{MnSymbolC}{m}{n}{
    <-6>  MnSymbolC5
   <6-7>  MnSymbolC6
   <7-8>  MnSymbolC7
   <8-9>  MnSymbolC8
   <9-10> MnSymbolC9
  <10-12> MnSymbolC10
  <12->   MnSymbolC12%
}{}
\DeclareMathSymbol{\powerset}{\mathord}{MnSyC}{180}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\input glyphtounicode.tex
\pdfgentounicode=1

\title{\texttt{timeline}: a Time Series Visualization Platform}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

%Single insitute
\author{Manuel Haid (1131404) \and Thomas Mauerhofer (1031957) \and Matthias Wölbitsch (1130899)}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{Institute}

\maketitle

\begin{abstract}
Abstract goes here
\end{abstract}

\keywords{...}

\section{Introduction}\label{sec:intro}

\section{Conclusion and Outlook}

\bibliographystyle{splncs03}
\bibliography{paper}

All links were last followed on October 5, 2014.

\end{document}

### 2016-06-09 docs/documentation/documentation.tex
added some basic infos for the report and added the stub for the documentation

\documentclass[11pt, a4paper]{article}

\usepackage{amssymb, amsmath}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{gensymb}

\author{Manuel Haid \and Thomas Mauerhofer \and Matthias Wölbitsch}
\title{\texttt{timeline} Documentation}

% content:
% it's about „Technical and code“ documentation (code)
% Requirements
% Libraries / frameworks used
% Which step/code does what in detail
% preferably with flow charts
% One should be able to extend or adapt your code easily after reading your documentation

\begin{document}

\maketitle
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intoduction}

\end{document}

### 2016-06-09 docs/documentation/documentation.tex
started to work on the doku changed numpy dependency to python standard library dependency

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction} \label{sec:intoduction}
 
+\section{Requirements} \label{sec:requirments}
+
+\begin{itemize}
+ \item \textgreater= Python 3.5
+\end{itemize}
+
+\section{Dependencies} \label{sec:dependencies}
+
+This section contains a description of all used external dependencies (e.g. libraries) and why they were used in this project.
+The python dependencies can be installed using \texttt{pip}, the Python package manager, using the \texttt{requirements.txt} file. 
+It is recommended to use a virtual environments when developing for this project to avoid conflicts with other system-wide installed versions of the same dependencies.
+
+\subsection{Back-end (Python)}
+
+\begin{description}
+ \item[Flask] 
+ Flask is a microframework (simple but extendable) for web development. 
+ It allows RESTful request dispatching and is well documented. 
+ In this project Flask is used for the rendering of the front-end using its template engine and providing an API for the supported visualizations.
+
+ \item[Pandas] 
+ Pandas is a widely used data analysis library. 
+ It provides data structures to efficiently store and query in-memory data. 
+ All temporal data (i.e. all time series) in this project is stored in Pandas DataFrame or Series objects.
+
+ \item[NumPy] 
+ NumPy is a powerful package for scientific computing. 
+ It provides efficient data structures and algorithms to operate on them. 
+ However, in this project this library is only used to sample random data for the example data sets and is therefore not very important. 
+\end{description}
+
+\subsection{Front-end (HTML5)}
+
+\begin{description}
+ \item[jQuery]
+ \item[MetricsGraphics.js]
+ \item[Bootstrap]
+\end{description}
+
 \end{document}

### 2016-06-09 timeline/visualizations.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python3
 # encoding: utf-8
 
-import numpy as np
+import math
 
 
 def time_series_plot(data_sets, start_date=None, end_date=None, **kwargs):
@@ -50,10 +50,10 @@ def auto_correlation_plot(data_set, max_lag, **kwargs):
         data.append({
             'lag': lag,
             'autocorrelation': data_set.data.autocorr(lag),
-            'plus95conf': z95 / np.sqrt(nsamples),
-            'plus99conf': z99 / np.sqrt(nsamples),
-            'minus95conf': -z95 / np.sqrt(nsamples),
-            'minus99conf': -z99 / np.sqrt(nsamples),
+            'plus95conf': z95 / math.sqrt(nsamples),
+            'plus99conf': z99 / math.sqrt(nsamples),
+            'minus95conf': -z95 / math.sqrt(nsamples),
+            'minus99conf': -z99 / math.sqrt(nsamples),
         })
 
     return {'title': 'ACF', 'data': data, 'x_accessor': 'lag',

### 2016-06-10 timeline/example_data_sets.py
added better forecast example dataset

@@ -34,21 +34,24 @@ def generate_random_live_data_set():
 def generate_internet_traffic_forecast():
     data = pd.read_csv('../datasets/internet-traffic-data.csv',
         parse_dates='Time', index_col='Time')
-    data = data / 8 / 2**30 # convert bits into GB
-    data.rename(columns={'Internet traffic data (in bits)': 'GB'},
-        inplace=True)
+    data = data / 8 / 2**30  # convert bits into GB
+    data = data['Internet traffic data (in bits)']
 
-    training_set = data['GB'][:'2005-07-13 23:59:59'].copy()
-    test_set = data['GB']['2005-07-14 00:00:00':].copy()
-    forecast_data = data['2005-07-14 00:00:00':].copy()
-    forecast_data.rename(columns={'GB': 'value'}, inplace=True)
-    forecast_data['value'] = 0.5
-    forecast_data['lower bound'] = forecast_data['value'] * 0.90
-    forecast_data['upper bound'] = forecast_data['value'] * 1.10
+    split_point = int(len(data) * 0.75)
+    training_set = data[:split_point]
+    test_set = data[split_point:]
+
+    forecast = pd.Series([data[t-1] for t in range(split_point, len(data))],
+        index=test_set.index, name='value')
+    upper_bound = forecast * 1.20
+    upper_bound.name = 'upper bound'
+    lower_bound = forecast * 0.80
+    lower_bound.name = 'lower bound'
+    prediction = pd.DataFrame([forecast, upper_bound, lower_bound]).transpose()
 
     return TimeSeriesForecast('Internet Traffic Forecast', 'A exemplary \
         forecast of the internet traffic of a private ISP.', training_set,
-        forecast_data, test_data=test_set, validation_split=1120780799)
+        prediction, validation_split=1120780799)
 
 def load_internet_traffic_data_set():
     data = pd.read_csv('../datasets/internet-traffic-data.csv',

### 2016-06-10 docs/documentation/documentation.tex
added some additional documentation

@@
 The python dependencies can be installed using \texttt{pip}, the Python package manager, using the \texttt{requirements.txt} file. 
-It is recommended to use a virtual environments when developing for this project to avoid conflicts with other system-wide installed versions of the same dependencies.
+It is recommended to use a virtual environment when developing for this project to avoid conflicts with other system-wide installed versions of the same dependencies.
 
@@
 \begin{description}
- \item[jQuery]
- \item[MetricsGraphics.js]
- \item[Bootstrap]
+ \item[jQuery] jQuery is the feature rich JavaScript library to simplify client-side scripting. 
+ In this project it is mainly used for AJAX calls.
+ \item[MetricsGraphics.js] MetricsGraphics.js is used to render the time series visualizations.
+ It is based on the well-known D3.js graphic library and provides all necessary primitives and features to plot the required figures.
+ \item[Bootstrap] This CSS framework is used to for its beautiful design templates to provide a familiar and responsive user interface.
+ Furthermore, some bootstrap add-ons were used for additional widgets (e.g. the bootstrap datetime picker).
 \end{description}

### 2016-06-11 docs/report/paper.tex
added some basic infos for the report and added the stub for the documentation
added first draft for the introduction in the paper

@@
 
-%introduce \powerset - hint by http://matheplanet.com/matheplanet/nuke/html/viewtopic.php?topic=136492&post_id=997377
-\DeclareFontFamily{U}{MnSymbolC}{}
-\DeclareSymbolFont{MnSyC}{U}{MnSymbolC}{m}{n}
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-    <-6>  MnSymbolC5
-   <6-7>  MnSymbolC6
-   <7-8>  MnSymbolC7
-   <8-9>  MnSymbolC8
-   <9-10> MnSymbolC9
-  <10-12> MnSymbolC10
-  <12->   MnSymbolC12%
-}{}
-\DeclareMathSymbol{\powerset}{\mathord}{MnSyC}{180}
-
 % correct bad hyphenation here
@@
 
-\title{\texttt{timeline}: a Time Series Visualization Platform}
-%If Title is too long, use \titlerunning
-%\titlerunning{Short Title}
-
-%Single insitute
-\author{Manuel Haid (1131404) \and Thomas Mauerhofer (1031957) \and Matthias Wölbitsch (1130899)}
-%If there are too many authors, use \authorrunning
-%\authorrunning{First Author et al.}
-\institute{Institute}
+\title{\texttt{timeline}: A Time Series Visualization Platform}
+\author{Manuel Haid \and Thomas Mauerhofer \and Matthias W\"olbitsch}
+\institute{Knowledge Technologies Institute}
 
@@
 
-\keywords{...}
+\keywords{Time Series, Visualization, Forecasting}
 
 \section{Introduction}\label{sec:intro}
+%Motivation and goals (which problem you are solving for the chosen data)
 
-\section{Conclusion and Outlook}
+In today's society data plays a import role in many different ways.
+For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand.
+Often time plays a essential role in these real-world data sets and applications. 
+The following list contains three representative examples in no particular order:
+
+\begin{enumerate}
+ \item The consumption of electricity does not only depend on the time of the day, but also on the day of the week and other seasonal effects.
+ It is important to model the future consumption to avoid failures of large portions or the complete power grid.
+ \item In the area of weather forecasting time is of the essence. 
+ Many applications (\eg shipping) require an precise and accurate forecasts to operate on minimal risk.
+ \item In the finance market many decisions are made within small time spans and are based on the prediction of complex models.
+ Incorrect or late data can lead to significant financial losses.
+\end{enumerate}
+
+This kind of data sets with an temporal importance are usually referred to as time series (\ie two- or higher-dimensional data with time as one dimension). 
+A more formal definition \cite{Cortez2012} of a time series \(\{Y\}_t\) is a time ordered collection of observations \((y_1, y_2, \ldots, y_n)\).
+A element of the time series recorded at time or period \(t\), denoted as \(y_t\), can either be a scalar value or a vector.
+Time series of scalars are denoted as \emph{univariate} times series, whereas a time series of higher dimensional data is called a \emph{multivariate} time series.
+For this project we only focused on univariate time series data and refer to to them simply as time series in the context of this paper.
+
+When dealing with time series usually one of the first steps in the analysis process is the visualization of the data.
+The graphical representation can already give some great insights in properties and characteristics of the data.
+For example, a simple visual inspection can show patterns, trends or seasonal effects without the use of advanced statistical methods. 
+These properties are important since they have to be considered in the modeling of the time series.
+One example for a statistical forecasting model that requires knowledge of the seasonal and stationary properties of a data set is Box--Jenkins \cite{Box1976} model.
+
+The goal of our project is to create a web-based platform that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.
+This includes, of course, the possibility to create simple time series plots (\ie visualizations that plot the data against the time) but also more advanced plots such as the auto-correlation function (ACF) plot.
+Another goal is the support of a quick and responsive visualization of forecasts on the a data set. 
+This means that is should be possible to quickly inspect the deviation of the prediction from the actual test data including a confidence band.
+
+The rest of the paper is structured as follows. 
+\Cref{sec:solution} contains a detailed description of our platform, used algorithms and overall design.
+\Cref{sec:conclusion} contains the conclusion of the project and a discussion of possible future work and improvements.
+
+\section{Solution}\label{sec:solution}
+%Description of your solution: methodology, algorithms, design, use case
+
+\section{Conclusion and Outlook}\label{sec:conclusion}
+% Discussion and outlook: what worked well, what could be improved
 
@@
 
-All links were last followed on October 5, 2014.
+All links were last followed on October 5, 2014. % TODO: change if there are any web ressources
 

### 2016-06-12 example.py
timeline now works as module

@@ -1,0 +1,19 @@
+#!/usr/bin/env python3
+# encoding: utf-8
+
+import timeline.app as app
+import timeline.data_sets as data_sets
+import timeline.example_data_sets as examples
+
+
+def example():
+    data_sets.register_data_set(examples.generate_random_data_set())
+    data_sets.register_data_set(examples.generate_random_data_set())
+    data_sets.register_data_set(examples.load_internet_traffic_data_set())
+    data_sets.register_live_data_set(examples.generate_random_live_data_set())
+    data_sets.register_forecast(examples.generate_internet_traffic_forecast())
+    app.app.run(host='0.0.0.0', debug=True)
+
+
+if __name__ == '__main__':
+    example()

### 2016-06-12 timeline/api.py

@@ -3,8 +3,8 @@
 import json
 from datetime import datetime
 from flask import Blueprint, request, Response, abort
-from data_sets import get_data_set, get_live_data_set, get_forecast
-from visualizations import (
+from .data_sets import get_data_set, get_live_data_set, get_forecast
+from .visualizations import (
     time_series_plot, add_rolling_mean, add_rolling_std, auto_correlation_plot,
     forecasting_eval_plot, build_data_object
 )

### 2016-06-12 timeline/app.py

@@ -2,21 +2,9 @@
 # encoding: utf-8
 
 from flask import Flask
-from frontend import frontend
-from api import api
-import example_data_sets as examples
-import data_sets
-
+from .frontend import frontend
+from .api import api
 
 app = Flask(__name__)
 app.register_blueprint(frontend)
 app.register_blueprint(api, url_prefix='/api')
-
-if __name__ == '__main__':
-    data_sets.register_data_set(examples.generate_random_data_set())
-    data_sets.register_data_set(examples.generate_random_data_set())
-    data_sets.register_data_set(examples.load_internet_traffic_data_set())
-    data_sets.register_live_data_set(examples.generate_random_live_data_set())
-    data_sets.register_forecast(examples.generate_internet_traffic_forecast())
-
-    app.run(host='0.0.0.0', debug=True)

### 2016-06-12 timeline/example_data_sets.py

@@ -1,13 +1,18 @@
 #!/usr/bin/env python3
 # encoding: utf-8
 
+import os
 import threading
 import datetime
 import time
 import pandas as pd
 import numpy as np
-from data_sets import TimeSeries, LiveTimeSeries, TimeSeriesForecast
+from .data_sets import TimeSeries, LiveTimeSeries, TimeSeriesForecast
 
+
+def _get_example_data_set_path():
+    this_dir, this_filename = os.path.split(__file__)
+    return os.path.join(this_dir, 'datasets', 'internet-traffic-data.csv')
 
 class LiveRandomData(LiveTimeSeries):
     def __init__(self):
@@ -32,8 +37,8 @@ def generate_random_live_data_set():
     return LiveRandomData()
 
 def generate_internet_traffic_forecast():
-    data = pd.read_csv('../datasets/internet-traffic-data.csv',
-        parse_dates='Time', index_col='Time')
+    data = pd.read_csv(
+        _get_example_data_set_path(), parse_dates='Time', index_col='Time')
     data = data / 8 / 2**30  # convert bits into GB
     data = data['Internet traffic data (in bits)']
 
@@ -54,9 +59,9 @@ def generate_internet_traffic_forecast():
         prediction, validation_split=1120780799)
 
 def load_internet_traffic_data_set():
-    data = pd.read_csv('../datasets/internet-traffic-data.csv',
-        parse_dates='Time', index_col='Time')
-    data = data / 8 / 2**30 # convert bits into GB
+    data = pd.read_csv(
+        _get_example_data_set_path(), parse_dates='Time', index_col='Time')
+    data = data / 8 / 2**30  # convert bits into GB
     data.rename(columns={'Internet traffic data (in bits)':
                          'Internet traffic data (in GB)'}, inplace=True)
 

### 2016-06-12 timeline/frontend.py

@@ -1,7 +1,7 @@
 # encoding: utf-8
 
 from flask import Blueprint, render_template
-from data_sets import (
+from .data_sets import (
     get_data_set, get_live_data_set, get_forecast, get_all_data_sets,
     get_all_live_data_sets, get_all_forecasts
 )

### 2016-06-12 vagrant/config/shell/start_backend.sh

@@ -12,6 +12,5 @@ source ~/venv/bin/activate
 echo "install requirements using pip"
 pip install -r requirements.txt
 
-echo "start timeline server on port 5000"
-cd /timeline/git/timeline
-python3.5 app.py > ~/timelinelogs/timeline_"$(date +"%Y%m%d_%H%M%S")" 2>&1 &
+echo "start timeline example"
+python3.5 example.py > ~/timelinelogs/timeline_"$(date +"%Y%m%d_%H%M%S")" 2>&1 &

### 2016-06-12 docs/documentation/documentation.tex
documentation

@@
 
-\section{Dependencies} \label{sec:dependencies}
+\section{Dependencies}\label{sec:dependencies}
 
@@
 
+\section{Modules}\label{sec:modules}
+
+\subsection{APP}
+This module simply creates the Flask object and resisters the routes for the front-end and for the API.
+The Flask object must be used to start timeline using the \texttt{run} method of the app object. 
+The source code is located in the \texttt{app.py} file.
+
+\subsection{API}
+The task of this module is to take requests from the front-end in form of AJAX calls and return the visualization primitives for the MetricsGraphics.js library as JSON objects.
+The source code is located in the \texttt{api.py} file.
+
+\subsubsection*{Time Series Plot: \texttt{api/time\_plot/\{time\_series\_id\}}}
+\begin{itemize}
+ \item[] \textbf{Method:} GET 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple time plot (i.e. a time plot of only one time series).
+ It takes the identifier of the time series as part of the URL (e.g. \texttt{api/time\_plot/42}) and can take additional parameter.
+ It may return a HTTP status code 404 if no time series with the given identifier exists and a HTTP status code 400 for invalid values for the optional GET parameter.
+ \item[] \textbf{Additional Parameter:} All of the following parameter are optional.
+ It is possible to only retrieve a slice of the time series using the \texttt{start\_date} and/or \texttt{end\_date} parameter.
+ Each of this parameter must be an integer, which represents to UNIX time stamp of the start time of the slice and the end time of the slice, respectively. 
+ Additional it is possible to add the graphs of the rolling mean and/or the rolling standard deviation to the plot.
+ The \texttt{rolling\_mean\_window} and \texttt{rolling\_std\_window} parameter must be integer that represent the number of samples that is used to calculate the running mean and standard deviation, respectively.
+\end{itemize}
+
+\subsubsection*{Time Series Plots: \texttt{api/time\_plots}}
+\begin{itemize}
+ \item[] \textbf{Method:} GET 
+ \item[] \textbf{Parameter:} list of time series ids
+ \item[] \textbf{Description:} 
+\end{itemize}
+
+\subsubsection*{Live Time Series Plot: \texttt{api/live\_plot/\{live\_time\_series\_id\}}}
+\begin{itemize}
+ \item[] \textbf{Method:} GET 
+ \item[] \textbf{Parameter:} last received
+ \item[] \textbf{Description:} 
+\end{itemize}
+
+\subsubsection*{ACF Plot: \texttt{api/acf\_plot/\{time\_series\_id\}}}
+\begin{itemize}
+ \item[] \textbf{Method:} GET 
+ \item[] \textbf{Parameter:} max lag, scale
+ \item[] \textbf{Description:} 
+\end{itemize}
+
+\subsubsection*{Forecasting Plot: \texttt{api/forecasting\_plot/\{forecast\_id\}}}
+\begin{itemize}
+ \item[] \textbf{Method:} GET 
+ \item[] \textbf{Parameter:} none
+ \item[] \textbf{Description:} 
+\end{itemize}
+
 \end{document}

### 2016-06-14 docs/report/paper.tex
documentation
work on the report

@@
 Therefore, it is good to have title printed on the pages, too.
-\documentclass[runningheads,a4paper]{llncs}
+\documentclass[runningheads,a4paper,11pt]{llncs}
 
@@
 \begin{abstract}
-Abstract goes here
+TODO
 \end{abstract}
@@
 In today's society data plays a import role in many different ways.
-For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand.
+For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand, or rely on it for operations entirely.
 Often time plays a essential role in these real-world data sets and applications. 
@@
  It is important to model the future consumption to avoid failures of large portions or the complete power grid.
+
  \item In the area of weather forecasting time is of the essence. 
- Many applications (\eg shipping) require an precise and accurate forecasts to operate on minimal risk.
+ Many applications (\eg shipping) require precise and accurate forecasts to operate on minimal risk.
+
  \item In the finance market many decisions are made within small time spans and are based on the prediction of complex models.
@@
 A more formal definition \cite{Cortez2012} of a time series \(\{Y\}_t\) is a time ordered collection of observations \((y_1, y_2, \ldots, y_n)\).
+This implies two trivial consequences. 
+First, the samples in the time series are ordered, and second, previous observations may influence future values but never the other way around.
 A element of the time series recorded at time or period \(t\), denoted as \(y_t\), can either be a scalar value or a vector.
@@
 These properties are important since they have to be considered in the modeling of the time series.
-One example for a statistical forecasting model that requires knowledge of the seasonal and stationary properties of a data set is Box--Jenkins \cite{Box1976} model.
+One example for a statistical forecasting model that requires knowledge of the seasonal and stationary properties of a data set is the Box--Jenkins \cite{Box1976} model.
 
-The goal of our project is to create a web-based platform that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.
+The goal of our project is it to create a web-based platform that allows the user to perform this initial visual inspection of the time series in a convenient but sophisticated way.
 This includes, of course, the possibility to create simple time series plots (\ie visualizations that plot the data against the time) but also more advanced plots such as the auto-correlation function (ACF) plot.
@@
 
+In the first step of our design process was the task to decide what types of data sets should be supported by our web-based platform.
+We decided that the following types are sufficient for the most time series analysis tasks:
+
+\begin{enumerate}
+ \item A simple time series data set. This consist mainly of a time indexed collection of scalar data points and meta data.
+ The meta data is mostly made up of some descriptive information (\ie the name of the data set and a description) and some other details about the data which can be directly derived from it (\eg the number of samples, the period,\ldots).
+
+ \item A specialized version of the simple time series data set were the data is not static but can be updated.
+ We denote this type of data set as live time series data set.
+ The meta data of the set is basically the same as for the simple time series data set, however, it provides special methods that allows the appending of new data samples at the end of the time series.
+ This type of data set is especially useful when dealing with data from live sources (\eg sensors).
+
+ \item A data set which can be used to investigate time series forecasts.
+ This object contains the same descriptive meta information as the simple time series data set as well, however, it differs in the actual data it can hold.
+ It basically separates a time series into multiple partitions. 
+ First, the training data that was used to train the forecasting algorithm and perhaps a time stamp which indices what portion of the training data was used as validation set to determine the performance during the training.
+ Furthermore, the prediction (\ie the forecasted time series) is the second part of the data set.
+ Optionally, there is should be the possibility to include the test data (\ie the actual values that should be predicted).
+\end{enumerate}
+
+After the types of the data sets were fixed, one of the most important design decisions for the project had to be made. 
+It was how the \texttt{timeline} platform should be used by the users.
+Our first idea was that the platform should be a standalone application.
+However, in our opinion, this causes some major usability and implementation issues.
+First, there is no nice and easy way to import the three different types data sets at the startup time from files.
+It would be very hard to specify a data format that can be utilized by all three data set types.
+For example, most of the real-world data sets are usually stored in the form form of \texttt{.csv} files.
+These typically do not allow the storage of additional meta information, at least not without special parsing rules.
+Furthermore, the live data sets would require a description of the live data source (\eg a socket) in some way and the forecasting data sets would either require multiple data files (\ie one for the training set, test set, and the prediction) or one file with multiple disjoint sections.
+
+Another possibility for the data import in the standalone application use case would be that the data can be imported using a dialog in the web-interface.
+However, since data sets can be quite large (\ie multiple thousand samples), the upload time could be substantive. 
+Moreover, since it was not planned to support persistent storage of the data sets in a rational or document-based database (at least not for the first release), the usability of the platform would suffer due to repeated re-uploads of the data sets.
+
+Therefore, we decided that the best way to use \texttt{timeline} would be as library. 
+This allows the user a much more flexible usage of the platform.
+We anticipate more or less the following workflow with \texttt{timeline} and designed the application such that it can be used in that way:
+
+\begin{enumerate}
+ \item The user works on a time series analysis or time series forecasting problem using Python or a Jupyter notebook.
+
+ \item The user wants to visualize some aspects of his or her work and imports the \texttt{timeline} library.
+
+ \item He creates one or more data set objects that corresponds to the problem he or she is working on and registers it within the library.
+
+ \item In the last step he or she can start the \texttt{timeline} web-service on a specific port and can visit the web-interface to view all available visualizations and other information.
+\end{enumerate}
+
+The usage of the platform as library also allows a simpler integration of live data sources by simply wrapping the data steam into a class that implements all required live data set methods.
+Altogether we think that this design choice supports a more natural and quicker workflow with the platform.
+
+Additionally, there are also some example data sets in the library available.
+It is possible to generate random data sets with 1000 data points that are sampled from a normal distribution with a random mean in the set \(\{0,1,\ldots,10\}\) and a random standard deviation in the range \([0,2]\).
+Furthermore, there is a internet traffic data set from the Time Series Data Library \cite{TSDL} available.
+There is a live data set that generates one new sample per second from a normal distribution with some random mean and standard deviation in the same ranges as before.
+And there is a simple forecasting data set available which is also based on the internet traffic data set.
+
 \section{Conclusion and Outlook}\label{sec:conclusion}
 % Discussion and outlook: what worked well, what could be improved
+
+% one problem: resultion of time only in seconds due to unix time stamp
 
@@
 
-All links were last followed on October 5, 2014. % TODO: change if there are any web ressources
-
 \end{document}

### 2016-06-15 docs/report/paper.tex

@@
 \begin{abstract}
-TODO
+In this paper a web-based visualization platform for time series data is proposed. 
+It is not only able to represent static temporal data and it properties but also data from live sources, such as sensors. 
+Furthermore, it allows the visualization of the output of time series prediction methods.
+The main aspects of this paper are the overall design, the use cases, and the outlook for possible enhancements of the application.
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-%Motivation and goals (which problem you are solving for the chosen data)
 
@@
 \section{Solution}\label{sec:solution}
-%Description of your solution: methodology, algorithms, design, use case
 
@@
 
-Another possibility for the data import in the standalone application use case would be that the data can be imported using a dialog in the web-interface.
+Another possibility for the data import in the standalone application use case would be the possibility to import the data using a dialog in the web-interface.
 However, since data sets can be quite large (\ie multiple thousand samples), the upload time could be substantive. 
@@
 
- \item He creates one or more data set objects that corresponds to the problem he or she is working on and registers it within the library.
+ \item He or she creates one or more \texttt{timeline} data set objects that corresponds to the problem he or she is working on and registers it within the library.
 
@@
 
-The usage of the platform as library also allows a simpler integration of live data sources by simply wrapping the data steam into a class that implements all required live data set methods.
+The usage of the platform as library also allows a simpler integration of live data sources by simply wrapping the data steam into a class that implements all required live data set methods and the possibility to simply include data sets from other web resources (\eg from a website that publishes stock market data).
 Altogether we think that this design choice supports a more natural and quicker workflow with the platform.
@@
 
+The visualization primitives that can be generated by the platform are the following:
+
+\begin{enumerate}
+ \item A simple time series plot, which plots the observations (i.e. the data points) against the time of the observations.
+ It is possible to filter the time series in a certain time span and include a rolling mean and rolling standard deviation into this plot.
+ This can be used to determine whether or not the time series is stationary \cite{Nason2006}.
+
+ \item A extended version of the simple time series plot that allows the plotting of multiple time series plots in one figure to compare them directly.
+
+ \item A extended version of the simple time series plot that works in the conjunction with live data sets such that it can be updated dynamically.
+
+ \item A autocorrelation plot \cite{Box1976}, also known as autocorrelation function (ACF) plot, which are a statistical tool to proof seasonal effects in the data.
+
+ \item A forecast evaluation plot, that can be used to inspect the performance a time series prediction method. 
+ It is a extended version of the simple time series plot as well, which shows the multiple parts of the forecast data set in one plot. 
+\end{enumerate}
+
+The back-end was implemented in Python using Flask \cite{Flask} as web-framework to render the user interface, deliver data using the API, and provide a small web-server such that the application can be executed.
+To store the time series data in the back-end the data analysis library Pandas \cite{McKinney2010} was used. 
+The application user interface uses the responsive Bootstrap \cite{Bootstrap} front-end framework and the JavaScript visualization library MetricsGraphics.js \cite{MetricsGraphics} to render the visualization primitives.
+
 \section{Conclusion and Outlook}\label{sec:conclusion}
-% Discussion and outlook: what worked well, what could be improved
 
-% one problem: resultion of time only in seconds due to unix time stamp
+Like in most other projects, there is a lot room for potential improvements and possible feature work.
+One constraint, due to the implementation of the framework, is that it only can handle dates and time stamps in a resolution of seconds.
+This is caused by the fact that all date and time related parameters are encoded using the UNIX time stamp (\ie the number of seconds since midnight January 1, 1970 UTC) before they are sent from the front-end to the back-end and vice versa.
+This is required since dates are often part of URLs, for example, in API requests.
+An implication of this is, of course, that it is only possible to handle time series data within a resolution of one second (\eg the period between two samples must be at least one second) in the \texttt{timeline} platform.
+This could be problematic, especially for real-time applications, where events usually happen in the range of milliseconds.
+However, there are potential solutions for this issue.
+For example, one option would be to encode dates as milliseconds since January 1, 1970 or a more general, and probable better, solution would be the usage of a well-defined date time format that allows the reliable parsing of dates from strings, which could be transmitted instead of the UINIX time stamp integers.
+
+Another possibility for feature work would be the creation of a Python package that can be uploaded to PyPI \cite{PyPI}, the Python package index.
+This would require to write a installer using the Python \texttt{setuptools} module. 
+Furthermore, the number of available visualizations is quite small at the time, and the existing plots could be more interactive (\eg brushing).
+There are plenty of other plots that could be integrated into the platform, for example, seasonality plots.
+However, not only additional visualizations could be added to the platform, but also algorithms and statistical tests that allow further examination of the data sets (\eg implementation of the Dickey--Fuller test \cite{Dickey1979}).
+
+In conclusion we think that the \texttt{timeline} visualization platform could be a valuable tool when doing time series analysis.
+It could easily integrated in existing workflows and is modular structured to allow enhancements. 
+There is room for potential improvements, but the first version of this application lays a solid foundation for future use cases.
 

### 2016-06-16 docs/report/paper.tex
fixed some typos in the report

@@
 In this paper a web-based visualization platform for time series data is proposed. 
-It is not only able to represent static temporal data and it properties but also data from live sources, such as sensors. 
+It is not only able to represent static temporal data and its properties, but also data from live sources, such as sensors. 
 Furthermore, it allows the visualization of the output of time series prediction methods.
@@
 For instance, businesses are using large amount of data to predict consumer behavior to satisfy their demand, or rely on it for operations entirely.
-Often time plays a essential role in these real-world data sets and applications. 
+Often time plays a essential role in these real-world data sets and its applications. 
 The following list contains three representative examples in no particular order:
@@
 
-This kind of data sets with an temporal importance are usually referred to as time series (\ie two- or higher-dimensional data with time as one dimension). 
+This kind of data set with an temporal importance is usually referred to as time series (\ie two- or higher-dimensional data with time as one dimension). 
 A more formal definition \cite{Cortez2012} of a time series \(\{Y\}_t\) is a time ordered collection of observations \((y_1, y_2, \ldots, y_n)\).
@@
 First, the samples in the time series are ordered, and second, previous observations may influence future values but never the other way around.
-A element of the time series recorded at time or period \(t\), denoted as \(y_t\), can either be a scalar value or a vector.
+A element of the time series, recorded at time or period \(t\), denoted as \(y_t\), can either be a scalar value or a vector.
 Time series of scalars are denoted as \emph{univariate} times series, whereas a time series of higher dimensional data is called a \emph{multivariate} time series.
@@
 
-When dealing with time series usually one of the first steps in the analysis process is the visualization of the data.
+When dealing with time series, usually one of the first steps in the analysis process is the visualization of the data.
 The graphical representation can already give some great insights in properties and characteristics of the data.
-For example, a simple visual inspection can show patterns, trends or seasonal effects without the use of advanced statistical methods. 
-These properties are important since they have to be considered in the modeling of the time series.
-One example for a statistical forecasting model that requires knowledge of the seasonal and stationary properties of a data set is the Box--Jenkins \cite{Box1976} model.
+For example, a simple visual inspection can show patterns, trends, and seasonal effects without the use of advanced statistical methods. 
+These properties are important since they have to be considered in the modeling process.
+One example for a statistical forecasting model, that requires knowledge of the seasonal and stationary properties of a data set, is the Box--Jenkins \cite{Box1976} model.
 
@@
 The rest of the paper is structured as follows. 
-\Cref{sec:solution} contains a detailed description of our platform, used algorithms and overall design.
+\Cref{sec:solution} contains a detailed description of our platform, used algorithms, and overall design.
 \Cref{sec:conclusion} contains the conclusion of the project and a discussion of possible future work and improvements.
@@
 
-In the first step of our design process was the task to decide what types of data sets should be supported by our web-based platform.
-We decided that the following types are sufficient for the most time series analysis tasks:
+The first step of our design process was the task to decide what types of data sets should be supported by our web-based platform.
+We decided that the following types are sufficient for the most common time series analysis tasks:
 
@@
 It would be very hard to specify a data format that can be utilized by all three data set types.
-For example, most of the real-world data sets are usually stored in the form form of \texttt{.csv} files.
+For example, most of the real-world data sets are stored in the form form of \texttt{.csv} files.
 These typically do not allow the storage of additional meta information, at least not without special parsing rules.
@@
 
-The usage of the platform as library also allows a simpler integration of live data sources by simply wrapping the data steam into a class that implements all required live data set methods and the possibility to simply include data sets from other web resources (\eg from a website that publishes stock market data).
+The usage of the platform as library also allows a simpler integration of live data sources by simply wrapping the data stream into a class that implements all required live data set methods and the possibility to simply include data sets from other web resources (\eg from a website that publishes stock market data).
 Altogether we think that this design choice supports a more natural and quicker workflow with the platform.
@@
 
- \item A autocorrelation plot \cite{Box1976}, also known as autocorrelation function (ACF) plot, which are a statistical tool to proof seasonal effects in the data.
+ \item A autocorrelation plot \cite{Box1976}, also known as autocorrelation function (ACF) plot, which is a statistical tool to proof seasonal effects in the data.
 
- \item A forecast evaluation plot, that can be used to inspect the performance a time series prediction method. 
+ \item A forecast evaluation plot, that can be used to inspect the performance of a time series prediction method. 
  It is a extended version of the simple time series plot as well, which shows the multiple parts of the forecast data set in one plot. 
@@
 
-Like in most other projects, there is a lot room for potential improvements and possible feature work.
+Like in most other projects, there is a lot room for potential improvements and possible future work.
 One constraint, due to the implementation of the framework, is that it only can handle dates and time stamps in a resolution of seconds.
@@
 
-Another possibility for feature work would be the creation of a Python package that can be uploaded to PyPI \cite{PyPI}, the Python package index.
+Another possibility for future work would be the creation of a Python package that can be uploaded to PyPI \cite{PyPI}, the Python package index.
 This would require to write a installer using the Python \texttt{setuptools} module. 

### 2016-06-17 timeline/static/js/timeline.js
Added Liveplot

@@ -1,15 +1,23 @@
-var time_plot = function(event) {
-    var params = event.data;
+var intervalId;
+var live_params;
+var data;
+var last_date;
+var live_viz;
+
+function time_plot(target_id, params) {
+    show_empty_plot(target_id, 'loading');
 
     $.getJSON($SCRIPT_ROOT + '/api/time_plot/' + params.id, params, function(viz) {
         convert_data_array(viz);
 
         viz.full_width = true;
         viz.height = 400;
-        viz.target = $(params.target)[0];
         viz.right = 40;
+        viz.target = target_id;
 
         MG.data_graphic(viz);
+    }).fail(function() {
+        show_empty_plot(target_id, 'sorry, an error occurred');
     });
 };
 
@@ -30,72 +38,101 @@ function multiple_time_plots(target_id, data_sets) {
     });
 };
 
-var live_plot = function(event) {
-        var route = $SCRIPT_ROOT + '/api/live_plot/random_live';
+function updateLiveUpdate(params) {
+        if(params['time_delta'] !== undefined) {
+          live_params['time_delta'] = params['time_delta'];
+        }
+
+        if(params['max_size'] !== undefined) {
+          live_params['max_size'] = params['max_size'];
+        }
+};
+
+function stopLiveUpdate() {
+        clearInterval(intervalId);
+}
+
+function live_plot(target_id, params) {
+        show_empty_plot(target_id, 'loading');
+
+        var route = $SCRIPT_ROOT + '/api/live_plot/' + params.id;
         $.getJSON(route, function(viz) {
         convert_data_array(viz);
 
-        viz.width = 800;
+        viz.full_width = true;
         viz.height = 400;
         viz.right = 80;
-        viz.target = $('#live-plot-canvas')[0];
+        viz.target = target_id;
         viz.legend_target = '.legend';
         viz.transition_on_update = false;
-
+        live_viz = viz;
         MG.data_graphic(viz);
-        activateLiveUpdate(viz, 1000, {'max_size': -10, 'time_delta': 30 /* seconds */});
+        live_params = {'max_size': -10, 'time_delta': 30 /* seconds */}
+        activateLiveUpdate(route, live_viz, 1000);
+    }).fail(function() {
+        show_empty_plot(target_id, 'sorry, an error occurred');
     });
-
-    function activateLiveUpdate(viz, interval, window) {
-        setInterval(function() {
-            var data = viz['data'][0];
[…]

### 2016-06-17 timeline/static/js/timeline.js
Bugfix timeline

@@ -52,6 +52,20 @@ function stopLiveUpdate() {
         clearInterval(intervalId);
 }
 
+function startLiveUpdate(data_id) {
+        var route = $SCRIPT_ROOT + '/api/live_plot/' + data_id;
+        activateLiveUpdate(route, live_viz, 1000);
+}
+
+function resetParams() {
+        clearInterval(intervalId);
+        intervalId = undefined;
+        live_params = undefined;
+        data  = undefined;
+        last_date = undefined;
+        live_viz  = undefined;
+}
+
 function live_plot(target_id, params) {
         show_empty_plot(target_id, 'loading');
 
@@ -73,11 +87,6 @@ function live_plot(target_id, params) {
         show_empty_plot(target_id, 'sorry, an error occurred');
     });
 };
-
-function startLiveUpdate(data_id) {
-        var route = $SCRIPT_ROOT + '/api/live_plot/' + data_id;
-        activateLiveUpdate(route, live_viz, 1000);
-}
 
 function activateLiveUpdate(route, viz, interval) {
         intervalId = setInterval(function() {
@@ -107,8 +116,7 @@ function activateLiveUpdate(route, viz, interval) {
             }
             viz['data'][0].push.apply(viz['data'][0], new_data);
             MG.data_graphic(viz);
-        }).fail(function() {
-            show_empty_plot(target_id, 'sorry, an error occurred');
+            console.log(live_params);
         });
     }, interval);
 };

### 2016-06-17 timeline/static/js/timeline.js
added css

@@ -81,7 +81,7 @@ function live_plot(target_id, params) {
         viz.transition_on_update = false;
         live_viz = viz;
         MG.data_graphic(viz);
-        live_params = {'max_size': -10, 'time_delta': 30 /* seconds */}
+        live_params = {'max_size': -10, 'time_delta': -30 /* seconds */}
         activateLiveUpdate(route, live_viz, 1000);
     }).fail(function() {
         show_empty_plot(target_id, 'sorry, an error occurred');
@@ -116,7 +116,7 @@ function activateLiveUpdate(route, viz, interval) {
             }
             viz['data'][0].push.apply(viz['data'][0], new_data);
             MG.data_graphic(viz);
-            console.log(live_params);
+            //console.log(live_params);
         });
     }, interval);
 };

### 2016-06-17 docs/documentation/documentation.tex
documentation

@@
 \section{Introduction} \label{sec:intoduction}
+
+In this section we want to explain how to start our project.
+
+\begin{itemize}
+\item
+\textbf{go to the vagrant folder:} \texttt{cd vagrant/}
+\item
+\textbf{start vagrant:} \texttt{vagrant up}
+\item
+\textbf{start our website:} start a browser and go to \texttt{http://localhost:5000/}
+\end{itemize}
+
+Now our website should start and you can explore it.
 
@@
  \item[] \textbf{Parameter:} list of time series ids
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple time plot (i.e. a time plot of all time series).
+ It may return a HTTP status code 404 if no time series with the given identifier exists.
 \end{itemize}
@@
  \item[] \textbf{Parameter:} last received
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple live time plot.
+ It may return a HTTP status code 404 if no time series with the given identifier exists.
+ The \texttt{last\_received} parameter must be integer that represent the last received timestamp, the start date and the new data.
 \end{itemize}
@@
  \item[] \textbf{Parameter:} max lag, scale
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple acf time plot.
+ It may return a HTTP status code 404 if no time series with the given identifier exists and a HTTP status code 400 for invalid values for the optional GET parameter.
+ \item[] \textbf{Additional Parameter:} All of the following parameter are optional.
+ It is possible to only retrieve a slice of the time series using the \texttt{max\_lag} parameter. The parameter must be an integer.
 \end{itemize}
@@
  \item[] \textbf{Parameter:} none
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple forecasting time plot.
+ It may return a HTTP status code 404 if no time series with the given identifier exists.
+\end{itemize}
+
+\subsection{DATA SETS}
+The task of this module is to get the values for the time series, live data and forecast data and store it in their classes.
+The source code is located in the \texttt{data\_sets.py} file.
+
+\subsubsection*{Register Data Sets:}
+\begin{itemize}
+ \item[] \textbf{Method:} ADD
+ \item[] \textbf{Description:} In this section, we have three functions to add the data set to the \texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast} dictionary.
+\end{itemize}
+
+\subsubsection*{Get Data Sets:}
+\begin{itemize}
+ \item[] \textbf{Method:} GET
+ \item[] \textbf{Description:} In this section, we have different functions to get the data sets (\texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast}). 
+ There are functions to get one data set (with an id) or you can get all data sets.
+\end{itemize}
+
+\subsubsection*{class TimeSeries:}
+\begin{itemize}
+ \item[] \textbf{Description:} The class TimeSeries needs an id, a name, a description, the data and the legend. 
+ It also has functions to get several informations like the number of samples, the start date, the end date and the period.
+\end{itemize}
+
+\subsubsection*{class LiveTimeSeries:}
+\begin{itemize}
+ \item[] \textbf{Description:} The class LiveTimeSeries needs a name, description and a legend.
+ It also has functions to get and to update the data.
+\end{itemize}
+
+\subsubsection*{class TimeSeriesForecast:}
+\begin{itemize}
+ \item[] \textbf{Description:} The class TimeSeriesForecast needs a name, a description, the training data, the forecasted data, the test data and the validation split.
+\end{itemize}
+
+\subsection{FRONT END}
+The task of this module is to render the different html templates.
+The source code is located in the \texttt{frontend.py} file.
+
+\subsection{VISUALIZATION}
+The task of this module is to visualize the data.
+The source code is located in the \texttt{visualizations.py} file.
+
+\subsubsection*{Time Series Plot}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with no additional given start and end date.
+\end{itemize}
+
+\subsubsection*{Add Rolling Mean}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling mean.
+\end{itemize}
+
+\subsubsection*{Add Rolling Std}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling standard deviation.
+\end{itemize}
+
+\subsubsection*{Auto Correlation Plot}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generate the data to visualize a auto correlation time series plot with the \texttt{max\_lag} parameter.
+\end{itemize}
+
+\subsubsection*{Forecasting Eval Plot}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generate the data to visualize a forecasting time series plot.
+\end{itemize}
+
+\subsubsection*{Build Data Object}
+\begin{itemize}
+ \item[] \textbf{Description:} This function build the object for all other functions in this class. The object consists of a date and a value.
 \end{itemize}

### 2016-06-17 docs/documentation/documentation.tex
update documentation

@@
 \item
-\textbf{start vagrant:} \texttt{vagrant up}
+\textbf{start vagrant:} \texttt{vagrant up} (the first time can take a long time, because of the new downloaded and installed dependencies)
 \item
@@
 
-\subsubsection*{Time Series Plot}
+\subsubsection*{Time Series Plot:}
 \begin{itemize}
  \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with no additional given start and end date.
+We iterate through all data from the data set, the title will be set and we return a object with a title, the x accessor, the date, the y accessor, the value,
+the data, and the legend.
 \end{itemize}
 
-\subsubsection*{Add Rolling Mean}
+\subsubsection*{Add Rolling Mean:}
 \begin{itemize}
  \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling mean. 
+ We calculate the rolling mean and generate the data object with the data and the legend.
 \end{itemize}
 
-\subsubsection*{Add Rolling Std}
+\subsubsection*{Add Rolling Std:}
 \begin{itemize}
  \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling standard deviation. 
+ We calculate the rolling standard deviation and generate the data object with the data and the legend.
 \end{itemize}
 
-\subsubsection*{Auto Correlation Plot}
+\subsubsection*{Auto Correlation Plot:}
 \begin{itemize}
  \item[] \textbf{Description:} This function generate the data to visualize a auto correlation time series plot with the \texttt{max\_lag} parameter.
+ We iterate through all data from the data set in range from 1 to the \texttt{max\_lag} and generate the data object
 \end{itemize}
 
-\subsubsection*{Forecasting Eval Plot}
+\subsubsection*{Forecasting Eval Plot:}
 \begin{itemize}
@@
 
-\subsubsection*{Build Data Object}
+\subsubsection*{Build Data Object:}
 \begin{itemize}

### 2016-06-17 docs/documentation/documentation.tex
hopefully endversion documentation

--- 2016-06-12 docs/documentation/documentation.tex
@@
 \section{Introduction} \label{sec:intoduction}
+
+In this section we want to explain how to start our project.
+
+\begin{itemize}
+\item
+\textbf{go to the vagrant folder:} \texttt{cd vagrant/}
+\item
+\textbf{start vagrant:} \texttt{vagrant up} (the first time can take a long time, because of building the source)
+\item
+\textbf{start our program:} after vagrant has been started, you can access it from the outside with port 5000. 
+Start a browser and go to \texttt{http://localhost:5000/}
+\end{itemize}
+
+Now our example application should start and you can explore it.
 
@@
  \item[] \textbf{Parameter:} list of time series ids
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple time plot (i.e. a time plot of all time series).
+ It may return a HTTP status code 404 if one time series data doesn't exist.
 \end{itemize}
@@
  \item[] \textbf{Parameter:} last received
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple live time plot.
+ The first request from this function is without an parameter, because it only gets the data. These function with the optional 
+ parameter \texttt{last\_received} signaled only an update from the data.
+ It may return a HTTP status code 404 if no time series with the given identifier exists.
 \end{itemize}
@@
  \item[] \textbf{Parameter:} max lag, scale
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple acf plot.
+ It may return a HTTP status code 404 if no time series with the given identifier exists and a HTTP status code 400 for invalid values for the optional GET parameter.
+ It is possible to only retrieve a slice of the time series using the \texttt{max\_lag} parameter. The parameter must be an integer.
+ The second parameter \texttt{scale} is optional, if it is null, the plot will be autoscaled.
 \end{itemize}
@@
  \item[] \textbf{Parameter:} none
- \item[] \textbf{Description:} 
+ \item[] \textbf{Description:} This route create the visualization primitive for a simple forecasting plot.
+ It may return a HTTP status code 404 if no time series with the given identifier exists.
+\end{itemize}
+
+\subsection{DATA SETS}
+The task of this module is, to define the class that describes the data sets for the time series, live data and forecast data.
+It also has functions to add and get the data from the right classes like described below.
+The source code is located in the \texttt{data\_sets.py} file.
+
+\subsubsection*{Class TimeSeries:}
+\begin{itemize}
+ \item[] \textbf{Description:} The member variables from the class TimeSeries are the autogenerated id, a name, a description, the data and optional the legend. 
+ It also has functions to get several informations like the number of samples, the start date, the end date and the period.
+\end{itemize}
+
+\subsubsection*{Class LiveTimeSeries:}
+\begin{itemize}
+ \item[] \textbf{Description:} These class is derived from the class TimeSeries. It only has additional functions to get and to update the data.
+\end{itemize}
+
+\subsubsection*{Class TimeSeriesForecast:}
+\begin{itemize}
+ \item[] \textbf{Description:} These class is also derived from the class TimeSeries. It only has additional member variables like 
+ the training data, the forecasted data, the test data and the validation split.
+\end{itemize}
+
+\subsubsection*{Register Data Sets:}
+\begin{itemize}
+ \item[] \textbf{Description:} In this section, we have three functions to add the data sets to the \texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast} dictionaries.
+\end{itemize}
+
+\subsubsection*{Get Data Sets:}
+\begin{itemize}
+ \item[] \textbf{Description:} In this section, we have different functions to get the data sets (\texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast}). 
+ There are functions to get one data set (with an id) or you can get all data sets.
+\end{itemize}
+
+\subsection{FRONT END}
+The task of this module is to render the different html templates, for example the info.html, index.html, multi\_time\_plots.html, live\_info.html, etc.
+
+\subsection{VISUALIZATION}
+The task of this module is to build the data so that the visualization library in the front end can show it.
+The source code is located in the \texttt{visualizations.py} file.
+
+\subsubsection*{Time Series Plot:}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with the optional parameter start and end date.
+An optional feature is, that if the data set is a list, multiple data sets will be used, otherwise only one data set will be used.
+Afterwards the title will be set and we return a object with a title, the x accessor, the date, the y accessor, the value,
+the data and the legend.
+\end{itemize}
+
+\subsubsection*{Add Rolling Mean:}
+\begin{itemize}
+ \item[] \textbf{Description:} This function adds a rolling mean line to the existing plot. 
+ We calculate the rolling mean and add the data object with the data and the legend to the existing data set.
+\end{itemize}
+
+\subsubsection*{Add Rolling Std:}
+\begin{itemize}
+ \item[] \textbf{Description:} This function adds a rolling standard deviation to the existing plot. 
+ We calculate the rolling standard deviation and add the data object with the data and the legend to the existing data set.
+\end{itemize}
+
+\subsubsection*{Auto Correlation Plot:}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generates an auto correlation for an existing data set. The \texttt{max\_lag} parameter 
+ describes the max number of correlation steps.
+\end{itemize}
+
+\subsubsection*{Forecasting Eval Plot:}
+\begin{itemize}
+ \item[] \textbf{Description:} This function generates the visualisation primitives.
+\end{itemize}
+
+\subsubsection*{Build Data Object:}
+\begin{itemize}
+ \item[] \textbf{Description:} This function converts the time series data to the right format, so that the visualization library can use it. The object consists of a date and a value.
 \end{itemize}

### 2016-06-17 docs/documentation/documentation.tex
documentation

@@
 
-% content:
-% it's about „Technical and code“ documentation (code)
-% Requirements
-% Libraries / frameworks used
-% Which step/code does what in detail
-% preferably with flow charts
-% One should be able to extend or adapt your code easily after reading your documentation
-
 \begin{document}
@@
 
-In this section we want to explain how to start our project.
+In this section we want to explain how to start a example that uses the \texttt{timeline} platform using vagrant.
 
-\begin{itemize}
-\item
-\textbf{go to the vagrant folder:} \texttt{cd vagrant/}
-\item
-\textbf{start vagrant:} \texttt{vagrant up} (the first time can take a long time, because of building the source)
-\item
-\textbf{start our program:} after vagrant has been started, you can access it from the outside with port 5000. 
-Start a browser and go to \texttt{http://localhost:5000/}
-\end{itemize}
-
-Now our example application should start and you can explore it.
+\begin{enumerate}
+\item Start vagrant using the \texttt{vagrant up} command.
+\item Get a cup of coffee, because the first startup requires the installation of some libraries from source and this may take a while.
+\item After that you can access the example from outside the vagrant box using port 5000 (i.e., open \url{http://localhost:5000/}).
+\end{enumerate}
 
@@
 This section contains a description of all used external dependencies (e.g. libraries) and why they were used in this project.
-The python dependencies can be installed using \texttt{pip}, the Python package manager, using the \texttt{requirements.txt} file. 
+The Python dependencies can be installed using \texttt{pip}, the Python package manager, using the \texttt{requirements.txt} file. 
 It is recommended to use a virtual environment when developing for this project to avoid conflicts with other system-wide installed versions of the same dependencies.
@@
  \item[] \textbf{Method:} GET 
- \item[] \textbf{Parameter:} list of time series ids
- \item[] \textbf{Description:} This route create the visualization primitive for a simple time plot (i.e. a time plot of all time series).
- It may return a HTTP status code 404 if one time series data doesn't exist.
+ \item[] \textbf{Parameter:} list of time series identifier
+ \item[] \textbf{Description:} This route creates the visualization primitive for a multi time series plot (i.e. a time plot of multiple time series).
+ It may return a HTTP status code 404 if one or more time series are not found in the data storage.
 \end{itemize}
@@
  \item[] \textbf{Description:} This route create the visualization primitive for a simple live time plot.
- The first request from this function is without an parameter, because it only gets the data. These function with the optional 
- parameter \texttt{last\_received} signaled only an update from the data.
+ The first request to this route must not contain the \texttt{last\_received} parameter, which is a UNIX time stamp.
+ All other requests on the same URL should contain this parameter to only obtain a update on the time series data. 
  It may return a HTTP status code 404 if no time series with the given identifier exists.
@@
  \item[] \textbf{Parameter:} max lag, scale
- \item[] \textbf{Description:} This route create the visualization primitive for a simple acf plot.
+ \item[] \textbf{Description:} This route creates the visualization primitive for a autocorrelation function plot.
  It may return a HTTP status code 404 if no time series with the given identifier exists and a HTTP status code 400 for invalid values for the optional GET parameter.
- It is possible to only retrieve a slice of the time series using the \texttt{max\_lag} parameter. The parameter must be an integer.
- The second parameter \texttt{scale} is optional, if it is null, the plot will be autoscaled.
+ The \texttt{max\_lag} parameter is required. It determines the number of autocorrelations offsets that should be included into the plot.
+ The parameter must be an integer.
+ The second parameter \texttt{scale} is optional, if it is null, the y-axis of the plot will be scaled automatically.
 \end{itemize}
@@
 \subsection{DATA SETS}
-The task of this module is, to define the class that describes the data sets for the time series, live data and forecast data.
-It also has functions to add and get the data from the right classes like described below.
+The task of this module is, to define the classes that describe the data sets for the time series, live data and forecast data.
+It also has functions to add and get the data sets from the from the storage.
 The source code is located in the \texttt{data\_sets.py} file.
@@
 \begin{itemize}
- \item[] \textbf{Description:} The member variables from the class TimeSeries are the autogenerated id, a name, a description, the data and optional the legend. 
- It also has functions to get several informations like the number of samples, the start date, the end date and the period.
+ \item[] \textbf{Description:} The member variables from the class TimeSeries are the auto-generated id, a name, a description, the data and optional the legend. 
+ It also has functions to get information like the number of samples, the start date, the end date and the period.
 \end{itemize}
@@
 \begin{itemize}
- \item[] \textbf{Description:} In this section, we have three functions to add the data sets to the \texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast} dictionaries.
+ \item[] \textbf{Description:} In this section, we have three functions to add the data sets to the \texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast} dictionaries for storage.
 \end{itemize}
@@
 \subsection{FRONT END}
-The task of this module is to render the different html templates, for example the info.html, index.html, multi\_time\_plots.html, live\_info.html, etc.
+The task of this module is to render the different HTML templates of the user interface (for example, the info.html, index.html, multi\_time\_plots.html, live\_info.html, etc).
 
 \subsection{VISUALIZATION}
-The task of this module is to build the data so that the visualization library in the front end can show it.
+The task of this module is to build the visualization objects so that the visualization library in the front end can render it.
 The source code is located in the \texttt{visualizations.py} file.
@@
 \begin{itemize}
- \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with the optional parameter start and end date.
+ \item[] \textbf{Description:} This function generates the visualization object for a time series plots, with the optional parameter start and end date.
 An optional feature is, that if the data set is a list, multiple data sets will be used, otherwise only one data set will be used.
@@
 \begin{itemize}
- \item[] \textbf{Description:} This function adds a rolling mean line to the existing plot. 
+ \item[] \textbf{Description:} This function adds a rolling mean line to the existing time series plot. 
  We calculate the rolling mean and add the data object with the data and the legend to the existing data set.
@@
 \begin{itemize}
- \item[] \textbf{Description:} This function adds a rolling standard deviation to the existing plot. 
+ \item[] \textbf{Description:} This function adds a rolling standard deviation to the existing time series plot. 
  We calculate the rolling standard deviation and add the data object with the data and the legend to the existing data set.
@@
 \begin{itemize}
- \item[] \textbf{Description:} This function generates an auto correlation for an existing data set. The \texttt{max\_lag} parameter 
+ \item[] \textbf{Description:} This function generates an auto correlation visualization primitive for an existing data set. The \texttt{max\_lag} parameter 
  describes the max number of correlation steps.
@@
 \begin{itemize}
- \item[] \textbf{Description:} This function generates the visualisation primitives.
+ \item[] \textbf{Description:} This function generates the visualization primitive for the forecast evaluation plot.
 \end{itemize}
@@
 \begin{itemize}
- \item[] \textbf{Description:} This function converts the time series data to the right format, so that the visualization library can use it. The object consists of a date and a value.
+ \item[] \textbf{Description:} This function converts the time series data to the right format, so that the visualization library can use it.
 \end{itemize}
